---
title: "Assessment-4"
author: "Veydant Katyal"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question-1

Download a dataset related to plants which are familiar in India and their diseases. Create multiple datasets (Tables) as per the requirement. (using DPLYR)

Perform the following operations using DPLYR core functions on the dataset and apply the joins wherever possible: 

# load all reuqired packages
```{r}
library(dplyr)
```

# load and inspect dataset
```{r}
plants_data <- read.csv("plant_disease_dataset_1.csv")
glimpse(plants_data)
head(plants_data)
```

# 1) Count the number of popular diseases. 

```{r}
disease_count <- plants_data %>%
  count(Disease, sort = TRUE)

print(disease_count)
```

# 2) Print the plants available in the states of India whose name starts with ‘A’. 

```{r}
plants_in_A_states <- plants_data %>%
  filter(grepl("^A", State, ignore.case = TRUE)) %>%
  select(Plant, State)

print(plants_in_A_states)

```

# 3) Create the tables for south states and north states data and perform all the joins. 

```{r}
south_states <- c("Andhra Pradesh", "Tamil Nadu", "Karnataka", "Kerala", "Telangana")
north_states <- c("Punjab", "Himachal Pradesh", "Uttar Pradesh", "Haryana", "Rajasthan", "Madhya Pradesh")

south_plants <- plants_data %>% filter(State %in% south_states)
north_plants <- plants_data %>% filter(State %in% north_states)

inner_join_data <- inner_join(south_plants, north_plants, by = "Disease", suffix = c("_South", "_North"))
left_join_data <- left_join(south_plants, north_plants, by = "Disease", suffix = c("_South", "_North"))
right_join_data <- right_join(south_plants, north_plants, by = "Disease", suffix = c("_South", "_North"))
full_join_data <- full_join(south_plants, north_plants, by = "Disease", suffix = c("_South", "_North"))

print(inner_join_data)
print(left_join_data)
print(right_join_data)
print(full_join_data)

```

# 4) Perform rename and mutate for common features in those tables(Q no c) 

```{r}
south_plants_renamed <- south_plants %>%
  rename(Plant_Name = Plant) %>%
  mutate(Severity_Level = case_when(
    Severity == "Mild" ~ "Low",
    Severity == "Moderate" ~ "Medium",
    Severity == "Severe" ~ "High"
  ))

north_plants_renamed <- north_plants %>%
  rename(Plant_Name = Plant) %>%
  mutate(Severity_Level = case_when(
    Severity == "Mild" ~ "Low",
    Severity == "Moderate" ~ "Medium",
    Severity == "Severe" ~ "High"
  ))

print(south_plants_renamed)
print(north_plants_renamed)

```

# 5) Write the user defined function for finding disease which are common in all the states and call it in summarise function
```{r}
find_common_diseases <- function(data) {
  data %>%
    group_by(Disease) %>%
    summarise(State_Count = n_distinct(State)) %>%
    filter(State_Count == n_distinct(plants_data$State)) %>%
    pull(Disease)
}

common_diseases <- find_common_diseases(plants_data)
print(common_diseases)
```

# 6) Get unique plant names for a specific feature using pipes.  

```{r}
unique_severe_plants <- plants_data %>%
  filter(Severity == "Severe") %>%
  distinct(Plant)

print(unique_severe_plants)
```

# 7) Apply the Group by function for mutated column in Q no d. 

```{r}
severity_grouped <- south_plants_renamed %>%
  group_by(Severity_Level) %>%
  summarise(Count = n())

print(severity_grouped)
```

# 8) Find out the second maximum and second minimum plant names which are affected by most of the diseases. 
```{r}
plant_disease_count <- plants_data %>%
  group_by(Plant) %>%
  summarise(Disease_Count = n()) %>%
  arrange(desc(Disease_Count))

second_max_plant <- plant_disease_count %>%
  slice(2) %>%
  pull(Plant)

second_min_plant <- plant_disease_count %>%
  slice(n() - 1) %>%
  pull(Plant)

print(paste("Second Maximum:", second_max_plant))
print(paste("Second Minimum:", second_min_plant))
```

# 9) Perform the functions suitable to ends-with, contains, one of, matches, everything, 

```{r}
filtered_plants <- plants_data %>%
  filter(endsWith(Plant, "a") | grepl("fruit", Plant, ignore.case = TRUE))

print(filtered_plants)
```

# 10) Apply rank function to the specific feature. 

```{r}
plants_data <- plants_data %>%
  mutate(Yield_Loss_Rank = rank(-Yield_Loss_Percentage, ties.method = "first"))

print(plants_data)
```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
